### 2024-11-23 Article/introduction.tex
updated intro

Then, the structure of this work is the following.
The first chapter is about basic concepts of category theory, such as categories, limits, constructions and adhesivity, that will be used to model the categories on which in the second chapter we will work on.
The prinicpal aim is to build up the categorial toolbox to work with. Category theory provides a general and uniform formalism, hence almost all definitions may seem very abstract, hence some concrete examples will be done.
The second chapter is entirely focused on graphs, starting from a general notion of graphs, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, source and target, which assign to each edge a source vertex and a target one.
The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization of them but also makes in evidence particular properties proper of graphs.
Then, we endow graphs with an equivalence relation among verices, to end up with an adhesivity result.
The last part is about e-graphs, and in particular their formalization and how they inherit certain properties from graphs with equivalences.

>>>>

The work is structured as follows.
The first chapter is about basic concepts of category theory, such as categories, limits, constructions and adhesivity, that will be used to model the categories on which in the second chapter we will work on.
The main aim is to build up the categorial toolbox to work with. 
Category theory provides a general and uniform formalism, hence almost all definitions may seem very abstract, however some concrete examples will be done.
The second chapter is entirely focused on graphs, starting from a general notion of graph, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, source and target, which assign to each edge a source vertex and a target one.
The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization of them but also makes in evidence particular properties proper of graphs.
Then, we endow graphs with an equivalence relation among vertices, to end up with an adhesivity result.
The last part is about e-graphs, and in particular their formalization and how they inherit certain properties from graphs with equivalences.
